---
title: "Cell type specific enrichment analysis with R (cseaR)"
subtitle: "created 2017-06-27; modified 2018-04-30"
author: "Alexis Norris" 
date: "`r Sys.Date()`"
output: 
  html_document:
    latex_engine: xelatex
    fig_caption: true
    fig_crop: false
    toc: true
    toc_depth: 2
    number_sections: true  
fontsize: 12pt
linkcolor: blue
urlcolor: blue
---

# Load genelists and dge (`limma`) results  
  * *resList* = list of data frames with *full* `limma` results for each test/comparison  
  * *geneList* = list of vectors each with *genes* (`HGNC symbols`) that are significant (e.g. FDR < 0.05) for each test/comparison  
  * Must be *HGNC symbols* (not other IDs or MGI symbols!)  
  * Using ranked & signed t-statistic, if using `edgeR` data, use LR (after signing it for direction)    

# Using significance cutoff (pSI, EWCE)

## Setup   
```{r sig_setup}
# Libraries -----------------------------------------
library(pSI)
library(EWCE)

# Functions -----------------------------------------
### Get genes driving EWCE overlap
ewce.getgenes <- function (hitGenes, sct_data) {
  ValidGenes = rownames(sct_data$cell_dists)[rownames(sct_data$cell_dists) %in% hitGenes]
  temp = sct_data$cell_dists[ValidGenes, ]
  return(temp)
}

# Cell data -----------------------------------------
load("input/pSI_celldata.rda") # psi_barresHg, psi_barresMm, psi_darmanis_celltype, psi_lakeCelltype, psi_linn, psi_linnSub
```

## pSI 

### Human celldata

#### Remove genes not in the celldata
```{r sig_psi_human_check}
# Darmanis --------------------------------------
### Change "-" to "." (e.g. HLA-DMB -> HLA.DMB) 
geneList_Darmanis <- lapply(geneList, function (x) gsub("\\-", "\\.", x))
geneList_Darmanis <- lapply(geneList_Darmanis, function (x) x[which(x %in% rownames(psi_darmanis_celltype))])

# Lake ------------------------------------------
geneList_Lake <- lapply(geneList, function (x) x[which(x %in% rownames(psi_lakeCelltype))])

# Barres Hg -------------------------------------
### Missing all March/Sept/Oct/Dec genes!
geneList_BarresHg <- lapply(geneList, function (x) x[which(x %in% rownames(psi_barresHg))])
```

#### Run stattests
```{r sig_psi_human_run}
res_psi <- list()

## Lake -----------------------------------------
for (i in names(geneList_Lake)) {
  set.seed(1116)
  res_psi$lake[[i]] = fisher.iteration(
    psi_lakeCelltype, 
    candidate.genes = geneList_Lake[[i]])
}

## Darmanis -------------------------------------
for (i in names(geneList_Darmanis)) {
  print(i)
  set.seed(1116)
  res_psi$darmanis2[[i]] <- fisher.iteration(
    psi_darmanis_celltype, 
    candidate.genes = geneList_Darmanis[[i]])
}

## Barres ---------------------------------------
for (i in names(geneList_BarresHg)) {
  set.seed(1116)
  res_psi$barresHg[[i]] <- fisher.iteration(
    psi_barresHg, 
    candidate.genes = geneList_BarresHg[[i]])
}
```

### Mouse celldata

#### Get mouse homologs  
```{r sig_mouse_convert}
load("input/HumanMouseGeneKey.rda")  # h2m

### Convert to mouse gene symbols
geneList_mouse <- lapply(geneList, function (x) {
  x <- h2m %>%
    filter(HGNC %in% x) %>%
    select(MGI) %>%
    unique() 
  na.omit(as.character(x$MGI))
})
```

#### Remove genes not in the celldata
```{r sig_psi_mouse_check}
# Linnarsson --------------------------------
geneList_Linn <- lapply(geneList_mouse, function (x) x[which(x %in% rownames(psi_linn))])

# Barres ------------------------------------
geneList_BarresMm <- lapply(geneList_mouse, function (x) x[which(x %in% rownames(psi_barresMm))])
```

#### Run stattests
```{r sig_psi_mouse_run}
# Linn Mouse -------------------------------------
for (i in names(geneList)) {
  set.seed(1116)
  res_psi$linnCell[[i]] <- fisher.iteration(
    psi_linn, 
    candidate.genes = geneList_Linn[[i]])
}

# Linn Mouse subtypes ----------------------------
for (i in names(geneList)) {
  set.seed(1116)
  res_psi$linnSub[[i]] <- fisher.iteration(
    psi_linnSub, 
    candidate.genes = geneList_Linn[[i]])
}

# Barres Mouse -----------------------------------
for (i in names(geneList)) {
  set.seed(1116)
  res_psi$barresMm[[i]] <- fisher.iteration(
    psi_barresMm, 
    candidate.genes = geneList_BarresMm[[i]])
}
```

### Unlist, clean, export
```{r sig_psi_wrangle}
### Unlist, export as table
res_psi_df <- do.call(rbind, lapply(res_psi, function (x) { # just results table
  df <- do.call(rbind, x)
  
  ### Cleanup colnames
  names(df) <- c("p0.05", "p0.01", "p0.001", "p0.0001")
  
  ### Separate into columns
  df$analysis_id <- gsub("\\..*", "", rownames(df))
  df$CellType <- gsub(".*\\.", "", rownames(df))
  df$Dir <- gsub(".*_", "", df$analysis_id)
  df$group <- gsub("_.*", "", df$analysis_id)
  
  ### Recalculate FDR
  df$p0.05_FDR <- p.adjust(df$p0.05, method = "BH")
  df$p0.01_FDR <- p.adjust(df$p0.01, method = "BH")
  df$p0.001_FDR <- p.adjust(df$p0.001, method = "BH")
  df$p0.0001_FDR <- p.adjust(df$p0.0001, method = "BH")
  
  ### Remove rownames and return df
  rownames(df) <- NULL
  df
})) 
res_psi_df$celldata <- gsub("\\..*", "", rownames(res_psi_df))
rownames(res_psi_df) <- NULL
readr::write_tsv(res_psi_df, "csea_pSI_all_df_long.tsv")
```

## EWCE

### Functions
```{r sig_ewce_fxns}
### Load required packages
library(EWCE)
library(biomaRt)
library(data.table)
library(pander)

### Setup parameters
reps <- 20000 # for publishing use 20000
```

### Updated EWCE fxns, to allow SUB-celltype testing too  
```{r sig_ewce_fxns}
### Fix function from EWCE
### version 2017-07-05
read_celltype_data2 <- function (path, exprstart_row = 3, celltype_row = 1, subtype_row = 2, e_min = 0.2, sample_colstart = 2, sample_colend = 252) 
{
  ### exprstart_row is first row with expression data
  ### Gene symbols are always the first column
  
  ### Darmanis (human SCT)
  #exprstart_row = 3, celltype_row = 1, subtype_row = 2, e_min = 0.2, sample_colstart = 2, sample_colend = 252, path = ????
  
  ### Linnarsson (mouse SCT), exprstart_row = 11, celltype_row = 8, subtype_row = 9, e_min = 0.2, sample_colstart = 3, sample_colend = 3007, path = ????
  
  ### Lake (human neuron SCT), exprstart_row = 5, celltype_row = 2, subtype_row = 3, e_min = 0.2, sample_colstart = 2, sample_colend = 3084, path = "AnnoData/Celltypes/Lake_HumanSCT_Science2016/Lake-2016_Gene_TPM_filtered_forEWCE.txt" # note that row 1 = neuron class (Ex vs In)

  if (!file.exists(path)) {
    stop("File does not exist. Must provide a valid path to the file containing cell type expression data")
  }
  else {
    expr_raw = read.csv(path, sep = "\t", stringsAsFactors = FALSE)
    gene_symbols = expr_raw[exprstart_row:dim(expr_raw)[1], 1] 
    if (!sum(duplicated(gene_symbols)) == 0) {
      stop("Expression file contains multiple rows with the same gene name. Duplicates are not permitted")
    }
    expr = expr_raw[exprstart_row:dim(expr_raw)[1], sample_colstart:sample_colend]
    cell_type = unlist(expr_raw[celltype_row, sample_colstart:sample_colend])
    cell_type = gsub("_", "", cell_type)
    subcell_type = sprintf(
      "%s_%s", cell_type, 
      unlist(expr_raw[subtype_row, sample_colstart:sample_colend]))
    matching_cell_type = as.character(unique(data.frame(
      cell_type = cell_type, subcell_type = subcell_type))[, "cell_type"])
    expr2 = as.numeric(as.matrix(expr))
    expr3 = matrix(as.numeric(
      as.matrix(expr)), nrow = nrow(expr), ncol = ncol(expr))
    rownames(expr3) = expr_raw[exprstart_row:dim(expr_raw)[1], 1]
    count = 0
    for (sct in unique(subcell_type)) {
      count = count + 1
      sub_expr = expr3[, subcell_type == sct]
      if (is.null(dim(sub_expr)) == TRUE) { 
        # for samples without replicates
        sct_expr = data.frame(temp = sub_expr)
      }
      else {
        # for samples with replicates
        sct_expr = data.frame(temp = apply(sub_expr, 1, mean))
      }
      colnames(sct_expr) = sct
      if (count == 1) {
        all_scts = sct_expr
      }
      else {
        all_scts = cbind(all_scts, sct_expr)
      }
    }
    rownames(all_scts) = rownames(expr3)
    keepGenes = rownames(all_scts)[apply(all_scts, 1, max) > e_min]
    all_scts = all_scts[keepGenes, ]
    cTs = unique(cell_type)
    geneList = unique(rownames(all_scts))
    count = 0
    for (gs in geneList) {
      count = count + 1
      exp1 = unlist(all_scts[gs, ])
      exp2 = exp1/sum(exp1)
      exp3 = data.frame(e = exp2, cell = matching_cell_type)
      exp4 = aggregate(exp3$e, sum, by = list(exp3$cell))
      exp5 = data.frame(t(exp4[, 2]))
      colnames(exp5) = as.character(exp4[, 1])
      rownames(exp5) = gs
      if (count == 1) {
        cell_dists = exp5
      }
      else {
        cell_dists = rbind(cell_dists, exp5)
      }
    }
    scTs = unique(subcell_type)
    geneList = unique(rownames(all_scts))
    count = 0
    for (gs in geneList) {
      count = count + 1
      exp1 = unlist(all_scts[gs, ])
      exp2 = data.frame(t(exp1/sum(exp1)))
      rownames(exp2) = gs
      if (count == 1) {
        subcell_dists = exp2
      }
      else {
        subcell_dists = rbind(subcell_dists, exp2)
      }
    }
    return(list(all_scts = all_scts, cell_dists = cell_dists, 
                subcell_dists = subcell_dists))
  }
}

bootstrap.enrichment.test.hg <- function (sct_data = NA, human.hits = NA, hg.bg = NA, reps = 20000, sub = FALSE) 
{ 
  control_related = prepare.genesize.control.network.hg(human.hits, hg.bg, numBOOT = reps)
  control_network = control_related[["list_network"]]
  hitGenes = control_related[["hitGenes"]]
  
  if (sub == TRUE) {
    bootstrap_data = matrix(0, ncol = length(colnames(sct_data$subcell_dists)), nrow = reps)
    cells = unique(colnames(sct_data$subcell_dists))
    hit.cells = subcell.list.dist.hg(hitGenes, sct_data)
  } 
  else {
    bootstrap_data = matrix(0, ncol = length(colnames(sct_data$cell_dists)), nrow = reps)
    cells = unique(colnames(sct_data$cell_dists))
    hit.cells = cell.list.dist.hg(hitGenes, sct_data)
  }
  for (s in 1:reps) {
    bootstrap_set = control_network[s, ]
    if (sub == TRUE) {
      bootstrap_data[s, ] = subcell.list.dist.hg(bootstrap_set, sct_data)
    }
    else {
      bootstrap_data[s, ] = cell.list.dist.hg(bootstrap_set, sct_data)
    }
  }
  count = 0
  for (ct in cells) {
    print(ct)
    count = count + 1
    if (sub == TRUE) {
      ct_boot_dist = bootstrap_data[, colnames(sct_data$subcell_dists) == ct]
      hit_sum = hit.cells[colnames(sct_data$subcell_dists) == ct]
    }
    else {
      ct_boot_dist = bootstrap_data[, colnames(sct_data$cell_dists) == ct]
      hit_sum = hit.cells[colnames(sct_data$cell_dists) == ct]
    }
    p = sum(ct_boot_dist >= hit_sum)/reps
    fold_change = hit_sum/mean(ct_boot_dist)
    sd_from_mean = (hit_sum - mean(ct_boot_dist))/sd(ct_boot_dist)
    if (sub == TRUE) {
      ct_root = gsub("_.*", "", ct)
    }
    else {
      ct_root = ct
    }
    if (p < 0.05) {
      print(sprintf("p-value = %s", p))
      print(sprintf("Fold enrichment = %s", fold_change))
      print(sprintf("Standard deviations from mean = %s", sd_from_mean))
    }
    if (count == 1) {
      results = data.frame(
        CellType = ct, 
        p = p, 
        fold_change = fold_change,   
        sd_from_mean = sd_from_mean)
    } 
    else {
      results = rbind(
        results,
        data.frame(
          CellType = ct, 
          p = p, 
          fold_change = fold_change, 
          sd_from_mean = sd_from_mean))
    }
    print("")
  }
  full_results = list(
    results = results, 
    hit.cells = hit.cells, 
    bootstrap_data = bootstrap_data)
  return(full_results)
}

prepare.genesize.control.network.hg <- function (human.hits, hg.bg, numBOOT = 20000, seed = 1116) 
{
  combined_human_genes = unique(c(human.hits, hg.bg))
  human <- useMart(
    #host = "www.ensembl.org", 
    host = "grch37.ensembl.org", 
    path = "/biomart/martservice",
    "ENSEMBL_MART_ENSEMBL",
    dataset = "hsapiens_gene_ensembl")
  hum_ens = getBM(
    attributes = c("hgnc_symbol", "ensembl_gene_id"), 
    filters = "hgnc_symbol", values = combined_human_genes, mart = human)
  all_lengths = getBM(
    attributes = c("transcript_length", "percentage_gene_gc_content", "ensembl_gene_id"), 
    filters = "ensembl_gene_id", values = hum_ens$ensembl_gene_id, mart = human)
  all_lengths = all_lengths[!is.na(all_lengths$transcript_length), ]
  all_lens = merge(all_lengths, hum_ens, by = "ensembl_gene_id")
  data_byGene = data.frame(data.table(all_lens)[ , lapply(.SD, mean), 
                                                 by = hgnc_symbol, .SDcols = 2:3])
  colnames(data_byGene) = c("HGNC.symbol", "transcript_lengths", 
                            "percentage_gc_content")
  data_byGene = data_byGene[data_byGene$HGNC.symbol != "", ]
  tl_quants = quantile(data_byGene$transcript_length, probs = seq(0.1, 1, 0.1))
  gc_quants = quantile(data_byGene$percentage_gc_content, probs = seq(0.1, 1, 0.1))
  quadrant = matrix(0, nrow = dim(data_byGene)[1], ncol = 2)
  colnames(quadrant) = c("TL", "GC")
  for (i in 1:dim(data_byGene)[1]) {
    quadrant[i,1] = which(data_byGene[i,2] < tl_quants)[1]
    quadrant[i,2] = which(data_byGene[i,3] < gc_quants)[1]
  }
  data_byGene$uniq_quad = sprintf("%s_%s", quadrant[,1], quadrant[,2])
  uq = data_byGene$uniq_quad
  data_byGene = data_byGene[uq != "2_NA" & uq != "NA_2" & uq != "3_NA", ]
  hitGenes_NEW = data_byGene[data_byGene$HGNC.symbol %in% human.hits,]$HGNC.symbol
  list_genes1d = human.hits[human.hits %in% data_byGene$HGNC.symbol]
  quad_genes = list()
  for (uq in unique(data_byGene$uniq_quad)) {
    quad_genes[[uq]] = unique(data_byGene[data_byGene$uniq_quad == uq,]$HGNC.symbol)
  }
  #print(dim(data_byGene))
  #print(length(hitGenes_NEW))
  list_network = matrix("", nrow = numBOOT, ncol = length(hitGenes_NEW))
  count = 0
  set.seed(seed)
  for (gene in hitGenes_NEW) {
    count = count + 1
    this_gene_quad = data_byGene[data_byGene$HGNC.symbol == gene, "uniq_quad"][1]
    #print(this_gene_quad)
    candidates = as.vector(unlist(quad_genes[this_gene_quad]))
    #print(candidates)
    list_network[ , count] = sample(candidates, numBOOT, replace = TRUE)
  }
  print("CONTROLLED BOOTSTRAPPING NETWORK GENERATED")
  return(list(hitGenes = hitGenes_NEW, list_network = list_network))
}

cell.list.dist.hg <- function (hitGenes, sct_data) 
{
  ValidGenes = rownames(sct_data$cell_dists)[rownames(sct_data$cell_dists) %in% hitGenes]
  temp = sct_data$cell_dists[ValidGenes, ]
  return(apply(temp, 2, sum))
}
  
subcell.list.dist.hg <- function (hitGenes, sct_data) 
{
  ValidGenes = rownames(sct_data$subcell_dists)[rownames(sct_data$subcell_dists) %in% hitGenes]
  temp = sct_data$subcell_dists[ValidGenes, ]
  return(apply(temp, 2, sum))
}
```

### Linnarsson Mouse SCT
```{r sig_ewce_mouse}
# Load linnarsson data --------------------------------------
data("celltype_data")

# Remove lists with <4 genes --------------------------------
sapply(geneList_Linn, length)
geneList_Linn <- geneList_Linn[lapply(geneList_Linn, length) > 3]

# Stattests for celltypes -----------------------------------
res_ewce <- list()
for (i in names(geneList_Linn)) {
  print(i)
  bgkd <- unique(setdiff(rownames(celltype_data$all_scts), 
                         geneList_Linn[[i]]))
  set.seed(1116); seed <- 1116
  res_ewce$linnCelltype[[i]] <- bootstrap.enrichment.test(
    sct_data = celltype_data, 
    reps = reps, 
    mouse.hits = geneList_Linn[[i]], 
    mouse.bg = bgkd,
    sub = FALSE
  )
}

# Stattests for cell subtypes -------------------------------
for (i in names(geneList_Linn)) {
  print(i)
  set.seed(1116); seed <- 1116
  res_ewce$linnSubtype[[i]] <- bootstrap.enrichment.test(
    sct_data = celltype_data, 
    reps = reps, 
    mouse.hits = geneList_Linn[[i]], 
    mouse.bg = bgkd,
    sub = TRUE
  )
}

# Unlist, export as table -----------------------------------
for (h in names(res_ewce)) for (i in names(res_ewce[[h]])) { 
  x <- as.data.frame(res_ewce[[h]][[i]]$results)
  x$analysis_id <- i
  x$CellType <- rownames(x)
  rownames(x) <- NULL
  x$FDR <- p.adjust(x$p, method = "BH")
  res_ewce[[h]][[i]] <- x
}

# combine the 2 analyses
res_ewce_df1 <- do.call(plyr::rbind.fill, res_ewce$linnCelltype)
res_ewce_df2 <- do.call(plyr::rbind.fill, res_ewce$linnSubtype)
res_ewce_df1$source <- "linnMmCelltype"
res_ewce_df2$source <- "linnMmSubtype"
res_ewce_df <- rbind(res_ewce_df1, res_ewce_df2)
```

### Lake Human SCT     
Run In1-8, Ex1-8 (celltypes) and In1-8, Ex1-8 * 6 BAs (subtypes)  
```{r sig_ewce_lake}
# Load ------------------------------------------------------
load("input/Lake-2016_Gene_TPM_filtered_forEWCE_sct_data.rda")

# Run -------------------------------------------------------
res_ewce_lake <- list()
for (i in names(geneList_Lake)) {
  print(i)
  hg_bgkd <- unique(setdiff(rownames(sct_data$all_scts), 
                            geneList_Lake[[i]]))
  set.seed(1116); seed <- 1116
  res_ewce_lake[[i]] <- bootstrap.enrichment.test.hg(
    sct_data = sct_data, 
    reps = reps, 
    human.hits = geneList_Lake[[i]], 
    hg.bg = hg_bgkd,
    sub = TRUE
  )
}

# Wrangle ------------------------------------------------
### Unlist, export as table
for (i in names(res_ewce_lake)) { 
  x <- as.data.frame(res_ewce_lake[[i]]$results)
  x$analysis_id <- i
  x$CellType <- rownames(x)
  rownames(x) <- NULL
  x$FDR <- p.adjust(x$p, method = "BH")
  res_ewce_lake[[i]] <- x
}
res_ewce_df <- do.call(plyr::rbind.fill, res_ewce_lake)
```

### Darmanis Human SCT  
```{r sig_ewce_darmanis}
# Load ------------------------------------------------------
load("input/DarmanisHumanEWCE_cortexonly_EWCE.rda")

# Run -------------------------------------------------------
res_ewce_darmanis <- list()
reps <- 20000
for (i in names(geneList_Darmanis)) {
  print(i)
  hg_bgkd <- unique(setdiff(rownames(sct_darmanis$all_scts), 
                            geneList_Darmanis[[i]]))
  set.seed(1116); seed <- 1116
  print(i)
  res_ewce_darmanis[[i]] <- bootstrap.enrichment.test.hg(
    sct_data = sct_darmanis, 
    reps = reps, 
    human.hits = geneList_Darmanis[[i]], 
    hg.bg = hg_bgkd,
    sub = FALSE
  )
}

# Wrangle ------------------------------------------------
### Unlist, export as table
for (i in names(res_ewce_darmanis)) { 
  x <- res_ewce_darmanis[[i]]$results
  x$analysis_id <- i
  rownames(x) <- NULL
  x$FDR <- p.adjust(x$p, method = "BH")
  res_ewce_darmanis[[i]] <- x
}
res_ewce_df <- do.call(plyr::rbind.fill, res_ewce_darmanis)
```

# Ranked  

## Modified from `phenoTest::GSEA`  
```{r ranked_phenoTest}
# Libraries ---------------------------------------------------
library(magrittr)
library(tidyr)
library(plyr)
library(dplyr)

# Load human cell data ----------------------------------------
### Uses pSI cutoffs of 0.05, 0.01, 0.001, and 0.0001
gsets <- readRDS("psi_celldata_geneSets_fcsea.rds")
sapply(gsets, length)

# Load dge results --------------------------------------------
resList # list of full-table results from limma for each test

# cse functions using phenoTest -------------------------------
#source("https://bioconductor.org/biocLite.R")
#biocLite("phenoTest")
stats <- lapply(resList, function (df) {
  df <- df[!is.na(df$feature_name), ] # feature_name = HGNC symbol
  df <- df[!is.na(df$t), ]
  df <- df[which(abs(df$t) > 0), ]
  df <- df[order(df$t, decreasing = TRUE), ]
  ### Note that duplicates (feature_name aka gene symbol) exist -- collapse by taking average in phenoTest::gsea
  x <- df$t
  names(x) <- df$feature_name
  x
})
stats <- append(stats, degStats)

### Run test
csea_res <- list()
for (h in names(stats)) {
  x <- stats[[h]]
  print(h)
  
  ### Remove celldata genes not in the universe of DGE features
  gsets2 <- lapply(gsets, function (celldata) {
    celldata[which(celldata %in% names(x))]
  })
  
  ### min/max filters
  gsets2 <- gsets2[which(lapply(gsets2, length) > 4)] # min 5 (default = 10)
  gsets2 <- gsets2[which(lapply(gsets2, length) < 2501)] # max 2500 (default = 500)
  
  ### Get this error if >10 gsets (gam method error): Error in norm(sm$X, type = "I") : LAPACK routines cannot be loaded
  ### gsea test, do in sets of 10 to avoid gam approxiation
  cseaData <- list()
  j <- 1
  print(length(gsets2))
  for (i in 1:(ceiling(length(gsets2)/10))) {
  k <- j + 9
  if (k > length(gsets2)) k = length(gsets2)
  cseaData[[i]] <- phenoTest::gsea(
    x, gsets2[j:k], 
    logScale = FALSE, 
    absVals = FALSE, 
    averageRepeats = TRUE, 
    B = 10000, 
    mc.cores = 1, 
    test = "perm", 
    p.adjust.method = "none",      # recalculate FDR with ALL genesets
    pval.comp.method = "original", # original or signed (default = original)
    pval.smooth.tail = TRUE, 
    minGenes = 5, maxGenes = 2500, 
    center = FALSE
  )$significance$summary           # extract results
  print(cseaData[[i]])             # print results
  j <- j + 10
  }
  
  ### Combine results
  cseaData <- as.data.frame(do.call(rbind, cseaData))
  
  ### Calculate FDR
  cseaData$fdr <- p.adjust(cseaData$pval.nes, "BH")
  
  ### Save to list
  csea_res[[h]] <- cseaData
}

### Clean, unlist, export
csea_res <- lapply(csea_res, function (df) {
  df <- as.data.frame(df)
  df$info <- gsub("\\.", "_", rownames(df))
  df$info <- gsub("0_05", "0.05", df$info)
  df$info <- gsub("0_01", "0.01", df$info)
  df$info <- gsub("0_001", "0.001", df$info)
  df$info <- gsub("1e-04pSI", "0.0001", df$info)
  df2 <- stringr::str_split_fixed(df$info, "_", 5)
  colnames(df2) <- c("source", "celltype", "subtype", "delete", "psi_cutoff")
  df3 <- cbind.data.frame(df2, df)
  df3$delete <- NULL
  df3
})
csea_res_df <- do.call(rbind, csea_res)
csea_res_df$analysis <- gsub("\\..*", "", rownames(csea_res_df))
readr::write_tsv(csea_res_df, "csea_ranked_results_all_table.tsv")
```

## [not updated!] Using `geneSetTest`   
```{r ranked_geneSetTest}
# Prepare dge/limma results -------------------------------------
### Take logFC for region with lowest FDR; Up/Down separately in case some genes have alternative splicing changes  
DupRemove <- function(df) {
  # Separate into up and down
  Dn <- subset(df, logFC < 0)
  Up <- subset(df, logFC > 0)
  # Sort by gene & pvalue (many have FDR=1), keep 1st of duplicate genes
  Dn <- Dn[order(Dn$Gene, Dn$FDR, Dn$PValue), ]
  Dn <- Dn[!duplicated(Dn$Gene), ]
  Up <- Up[order(Up$Gene, Up$FDR, Up$PValue), ]
  Up <- Up[!duplicated(Up$Gene), ]
  # Combine the two
  DnUp <- rbind.data.frame(Dn, Up)
}
results <- DupRemove(res)
results$Gene <- as.character(results$Gene)

#### Sign the statistic
results$signedLR <- ifelse(results$logFC < 0, -results$LR, results$LR)

# Load cell data ------------------------------------------------
celldata <- readRDS("psi_celldata_geneSets_fcsea.rds") # not sure this is correct for below!

# Run rank test -------------------------------------------------
library(limma)
res_Rank <- lapply(celldata, function(df) {
  names(df)
  lapply(df, function(x) {
    names(x)
    geneSetTest(index = ifelse(x %in% results$Gene, TRUE, FALSE), 
                statistics = results$signedLR)
  })
})

# Wrangling ------------------------------------------------
# Combine all results into one data frame
resRank <- data.frame("Source" = names(unlist(res_Rank)),
                      "PValue" = unlist(res_Rank))
# FDR adjust
resRank$FDR <- p.adjust(resRank$PValue, method = "BH")

# Print significant results
resRank_sig <- subset(resRank, PValue < 0.05)
rownames(resRank_sig) <- NULL
pander(resRank_sig)

# Print top 10
resRank_top <- resRank[order(resRank$PValue, decreasing = F), ][1:10, ]
rownames(resRank_top) <- NULL
print(resRank_top)
```

